%! Author = jonathan
%! Date = 5/25/25
\begin{dedication}
    \textit{To those who say yes—still—when everything else screams no.}
\end{dedication}

\begin{acknowledgements}
    First and foremost, I thank God—the Author of all things good—for sustaining me through every moment of this journey.
    He remained faithful in seasons of clarity and in shadows of doubt.
    Whatever merit this work holds is but a fragment of the grace I have received.

    To my advisor, \textbf{Dr. Rachee Singh}, thank you for the trust, the freedom, and the unwavering support!
    You gave me the space to think creatively, and your mentorship has been a true gift.
    I am especially grateful for your generosity, both professionally and personally.
    Your unique willingness to support your students holistically—academically and beyond—has
    helped me blossom as a well-rounded researcher.
    I also appreciate the lab resources (especially the GPUs) you made readily accessible.
    Much of the preliminary exploration and hypothesis testing for this research took place on them,
    and they contributed immense value to this thesis.

    To my minor field member, \textbf{Dr. Giulia Guidi}—thank you for being an excellent mentor
    and for your generosity with time and resources.
    Your provision of high-performance computing infrastructure made a tangible difference in this work,
    and I recognize the immense privilege it is to have had access to such powerful systems.

    To my second minor field member, \textbf{Dr. Chris De Sa}—I am deeply grateful for the opportunity to
    have learned Machine Learning Systems (MLSys) from you.
    Your passion and enthusiasm for the field is infectious, and your teaching is exceptional.
    If I could take your MLSys class again, I would in a heartbeat!

    To the \textbf{Christ Chapel Choir (’24/25)}—thank you for being my second family away from home.
    I joined you not knowing how to read sheet music, yet you welcomed me warmly and gave me room to grow rapidly.
    That kindness means more to me than I can express.
    One of my fondest memories was singing Handel’s \textit{Hallelujah Chorus} together; it was both exhilarating
    and quite fun!
    I am especially thankful to Dr.\ Art Ostrander (Choir Director) for his technical precision and leadership;
    Carrie Ostrander (Soprano);
    Dr.\ Debbie Martin (Alto and pianist);
    Jyying Juliana Kan (Soprano);
    Margaret Brodhead (Pianist); Jim and Cindy Van Duren (Bass and Soprano);
    Amy Blumenthal (Alto); and Debbie Axtell (Alto).
    You have all helped shape the slightly more competent musician and vocalist I am today.

    To my colleagues at Cornell who made this journey richer—
    the CS MS classes of ’24 and ’25, Dr.\ Singh’s research group,
    Julian Bellavita, and the broader systems community—thank you for the fun events, collaboration, and conversation.

    Finally, to my parents—your quiet strength and
    unwavering support have been immeasurably valuable to all my academic endeavors.
    I would not be here without you.
    Thank you.
\end{acknowledgements}